---
title: "Rolling_Stone_Analyze"
author: "Fang"
date: "12/3/2017"
output: md_document
---
```{r}

library(tidyr)
library(tidyverse)
library(ggplot2)
library(tidyr)
library(stringr)

#read data from github link
rolling_stone=read.csv("https://raw.githubusercontent.com/dahaohanbao/rolling_stone_data/master/albumlist.csv", header=TRUE)

#show the first 6 line from rolling_stone table
head(rolling_stone)

#write csv file to locial folder
write.csv(rolling_stone,file="/Users/Fang/Desktop/UBCcourses/522/rolling_stone_data/data/rolling_stone.csv")
```

```{r}
#read data file from locial folder
rolling_stone <- read.csv("/Users/Fang/Desktop/UBCcourses/522/rolling_stone_data/data/rolling_stone.csv")

#make a summary table for data set
summary_rolling_stone <- summary(rolling_stone)
summary_rolling_stone

#write this summary table to locial folder
write.csv(summary_rolling_stone,file="/Users/Fang/Desktop/UBCcourses/522/rolling_stone_data/results/summarized_rolling_stone.csv")

```

>We have 500 data in total. Top3 artist are Bob Dylan, The beatles and The Rolling Stones. Top 3 Genres are Rock Funk and Hiphop.


```{r,warning=FALSE}

rs <- read.csv("/Users/Fang/Desktop/UBCcourses/522/rolling_stone_data/data/rolling_stone.csv")

firstplot <- ggplot(rs,aes(Year))+
  geom_histogram()+
  ggtitle("Albums number via Year")
firstplot

rs$Genre <- rs$Genre %>% 
  str_replace("[[:punct:]]","") 

unique(rs$Genre1)
rs <- rs %>% 
  separate(Genre, into = c("Genre1","Genre2"), sep=" ") 


secondplot <- ggplot(rs,aes(Genre1))+
  geom_bar(aes(fill=Genre1))+
  ggtitle("Genre Distribution")
secondplot

thirdplot <- ggplot(rs,aes(x=Year))+
  geom_freqpoly(aes(color=Genre1))+
  ggtitle("Genre Distribution via Year")
thirdplot

ggsave("results/firstplot.pdf",firstplot)
ggsave("results/secondplot.pdf",secondplot)
ggsave("results/thirdlot.pdf",thirdplot)
```

>From the Albums unmber via Year plot, we can see that from 1965 to 1980 is the most productive age of rolling stone and in 1970 rolling stone released the most albums.

>From the Second plot, we can see that Rock music is the most music genre that released by rolling stone.

>From the third plot, we can see that rock music had big wave, which means that music genres that rolling stone release are different in different age.